Overview

### 2020-11-12 README.Rmd
Update README and citation info

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/chainsawriot/oolong.svg?branch=master)](https://travis-ci.org/chainsawriot/oolong)
[![Codecov test coverage](https://codecov.io/gh/chainsawriot/oolong/branch/master/graph/badge.svg)](https://codecov.io/gh/chainsawriot/oolong?branch=master)
<!-- badges: end -->

@@

>>>>

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/chainsawriot/oolong.svg?branch=master)](https://travis-ci.org/chainsawriot/oolong)
[![Codecov test coverage](https://codecov.io/gh/chainsawriot/oolong/branch/master/graph/badge.svg)](https://codecov.io/gh/chainsawriot/oolong?branch=master)
[![joss stataus](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62/status.svg)](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62)
[![zenodo](https://zenodo.org/badge/224468858.svg)](https://zenodo.org/badge/latestdoi/224468858)
[![CRAN status](https://www.r-pkg.org/badges/version/oolong)](https://CRAN.R-project.org/package=oolong)
<!-- badges: end -->

@@

## Citation

Please cite this package as:

Chan et al., (2020). oolong: An R package for validating  automated content analysis tools. Journal of Open Source Software, 5(55), 2461, [https://doi.org/10.21105/joss.02461](https://doi.org/10.21105/joss.02461)

For a BibTeX entry, use the output from `citation(package = "oolong")`.
